An example of extremely reproducible enrichment analysis.

### 2023-03-24 example.Rmd
update chart header

plot(log10(def$baseMean) ,def$log2FoldChange,
  cex=0.6,pch=19,col="darkgray",
  main="strict filter",
  xlab="log10(basemean)",ylab="log2(fold change)")

>>>>

plot(log10(def$baseMean) ,def$log2FoldChange,
  cex=0.6,pch=19,col="darkgray",
  main="5-azacitidine treatment in AML3 cells",
  xlab="log10(basemean)",ylab="log2(fold change)")
